\begin{frame}[allowframebreaks]{References}

    \begin{thebibliography}{}

        % Article is the default.
        \setbeamertemplate{bibliography item}[book]

        \bibitem{geron2022hands}
        Hands-on machine learning with Scikit-Learn, Keras, and TensorFlow
        \newblock G{\'e}ron Aur{\'e}lien.
        \newblock \emph{O'Reilly Media, Inc.}

        \bibitem{howard2020deep}
        Deep Learning for Coders with fastai and PyTorch
        \newblock Howard Jeremy and Gugger Sylvain.
        \newblock \emph{O'Reilly Media}

        \setbeamertemplate{bibliography item}[article]

        \bibitem{kulfan2008universal}
        Universal parametric geometry representation method
        \newblock Kulfan Brenda.
        \newblock \emph{Journal of aircraft}

        \bibitem{kulfan2010recent}
        Recent extensions and applications of the 'CST'universal parametric geometry representation method
        \newblock Kulfan Brenda.
        \newblock \emph{Cambridge University Press}

        \bibitem{kulfan2006fundamental}
        "Fundamental" parameteric geometry representations for aircraft component shapes
        \newblock Kulfan Brenda and Bussoletti John.
        \newblock \emph{11th AIAA/ISSMO multidisciplinary analysis and optimization conference}

        \bibitem{nelder1965simplex}
        A simplex method for function minimization
        \newblock Nelder John and Mead Roger.
        \newblock \emph{The British Computer Society, The computer journal}

        \bibitem{drela1998user}
        A User's Guide to MISES 2.63
        \newblock Drela Mark and Youngren Harold.
        \newblock \emph{Massachusetts Institute of Technology, Cambridge, MA}

        \bibitem{youngren1991viscous}
        Viscous/inviscid method for preliminary design of transonic cascades
        \newblock Youngren Harold and Drela Mark.
        \newblock \emph{27th Joint Propulsion Conference}

        \setbeamertemplate{bibliography item}[online]

        \bibitem{harris2020array}
        Array programming with NumPy
        \newblock \url{https://doi.org/10.1038/s41586-020-2649-2}
        \newblock \emph{Springer Science and Business Media {LLC}}

        \bibitem{2020SciPy-NMeth}
        SciPy: Fundamental Algorithms for Scientific Computing in Python
        \newblock \url{https://rdcu.be/b08Wh}
        \newblock \emph{Nature Methods}

        \bibitem{Hunter:2007}
        Matplotlib: A 2D graphics environment
        \newblock Hunter J. D.
        \newblock \emph{Computing in Science \& Engineering}

        \bibitem{reback2020pandas}
        pandas-dev/pandas: Pandas
        \newblock The pandas development team.
        \newblock \url{https://doi.org/10.5281/zenodo.3509134}

        % \bibitem{Vakil2006}
        % R.~Vakil.
        % \newblock \emph{The moduli space of curves and Gromov--Witten theory}, 2006.
        % \newblock \url{http://arxiv.org/abs/math/0602347}

        % \setbeamertemplate{bibliography item}[triangle]

        % \bibitem{AM1969}
        % M.~Atiyah and I.~Macdonald.
        % \newblock \emph{Introduction to commutative algebra}.
        % \newblock Addison-Wesley Publishing Co., Reading, Mass.-London-Don
        % Mills, Ont., 1969

        % \setbeamertemplate{bibliography item}[text]

        % \bibitem{Fraleigh1967}
        % J.~Fraleigh.
        % \newblock \emph{A first course in abstract algebra}.
        % \newblock Addison-Wesley Publishing Co., Reading, Mass.-London-Don Mills, Ont., 1967

    \end{thebibliography}
\end{frame}